Time slice analyses

### 2017-11-24 analyses/01-extract-data-for-analyses.Rmd
Quick fixes for Wright's tree and FADLAD

```{r}
slug <- "Wright2017"

@@

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length * 0.03517385

@@

>>>>

```{r}
source("../functions/tree.age.fossil.R")

slug <- "Wright2017"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
# FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
#TG: The FADLAD ages seems pretty weird, the data should be Ordovician/Devonian (-485/-360) and the range in these FADLADs is (-113/-10)!
#TG: I've thus replaced it by a dummy FADLAD for now (just the taxa age) (see line ~169 after root.time)
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

@@

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length / 0.03517385 #TG: following the note above, it's divide not multiply (i.e. increase branch length because rate < 0)

@@

# Dummy FADLAD
tree_ages <- tree.age.fossil(tree)[1:Ntip(tree),]
FADLAD <- as.data.frame(matrix(c(tree_ages$ages, tree_ages$ages), ncol = 2, byrow = FALSE, dimnames = list(as.character(tree_ages$elements), c("FAD", "LAD"))))

### 2017-11-24 analyses/02-time-slice-analyses-Wright2017.Rmd
Minor edits
Quick fixes for Wright's tree and FADLAD

## The latest version of dispRity on master branch
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)

## Load functions using source
# Doesn't always work... Rmd problem?
source("../functions/simulations_fun.R")
```

@@

## Loading the FADLAD
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

## Loading the tree
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))
## Adding node labels and a root age (max tree age date)
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- 485.4 # specific to Wright 2017 tree

>>>>

## The latest version of dispRity on release branch
## install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)

## Load functions using source
# Doesn't always work... Rmd problem?
source("../functions/simulations_fun.R")
source("../functions/tree.age.fossil.R")
```

@@

## Loading the FADLAD
# FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
```

TG: There's a problem with the FADLAD (too recent! - see 01-extract-data-for-analysis.Rmd lines ~150).
Also, I jus realised that the operations here are done twice, once in the extract-data file and once here.
The clever way would be to do everything in the extract-data (e.g. the root time, rescaling etc...) so that only the time slice analysis is done here.
We could export the data bundle (i.e. the `morphospace`, `tree` and `FADLAD`) in a `.Rda` format and simply load it here (so we're sure we have the correct root time etc.).

```{r}
#TG: Tree tinkering from 01-extract-data-for-analysis.Rmd

# Replace zero branches with minimu branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length / 0.03517385 #TG: following the note above, it's divide not multiply (i.e. increase branch length because rate < 0)

# Add root time: 485.4
tree$root.time <- 485.4

# Dummy FADLAD
tree_ages <- tree.age.fossil(tree)[1:Ntip(tree),]
FADLAD <- as.data.frame(matrix(c(tree_ages$ages, tree_ages$ages), ncol = 2, byrow = FALSE, dimnames = list(as.character(tree_ages$elements), c("FAD", "LAD"))))

# ## Loading the tree
# tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))
# ## Adding node labels and a root age (max tree age date)
# tree <- makeNodeLabel(tree, method = "number", prefix = "n")
# tree$root.time <- 485.4 # specific to Wright 2017 tree
